Determinants of Wage Variation in Canada

### 2024-12-14 paper/paper.qmd
fix prose

```{r fig.width=5, fig.height=5}
#| label: fig-education-level
#| fig-cap: "Average hourly wages in Canada by education level from 2000 to 2019. Each box represents the wage distribution for a specific education level, with higher education levels corresponding to higher median wages."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-gender
#| fig-cap: "Average hourly wages in Canada by gender from 2000 to 2019. Each violin plot represents the wage distribution for males and females, with males showing higher median wages and a broader range of earnings compared to females."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-age
#| fig-cap: "Average hourly wages in Canada by age group from 2000 to 2019. Each curve represents the wage distribution for a specific age group, with older age groups showing higher average wages and broader distributions compared to younger groups."
#| echo: false
#| warning: false

@@

```{r fig.width=10, fig.height=7}
#| label: fig-visualize-model
#| fig-cap: "Average hourly wages by education level, gender, and age group in Canada. Panels represent age groups, with points color-coded by gender. Dashed lines show linear trends, highlighting wage differences across education levels, genders, and age groups."
#| echo: false
#| warning: false

@@

We are conducting a survey to understand how demographic and educational factors influence hourly wages in Canada. Your participation is important, and your responses will contribute to valuable research on wage distribution across various groups.

@@

Your responses are valuable to us in understanding wage trends in Canada. If you have any questions or would like more information about this research, please feel free to contact us at [liuyuanyi1208@gmail.com](mailto:liuyuanyi1208@gmail.com).

>>>>

```{r fig.width=5, fig.height=5}
#| label: fig-education-level
#| fig-cap: "Average hourly wages in Canada by education level from 2000 to 2019. Higher education levels corresponding to higher median wages."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-gender
#| fig-cap: "Average hourly wages in Canada by gender from 2000 to 2019. Males showing higher median wages and a broader range of earnings compared to females."
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-age
#| fig-cap: "Average hourly wages in Canada by age group from 2000 to 2019. Older age groups showing higher average wages and broader distributions compared to younger groups."
#| echo: false
#| warning: false

@@

```{r fig.width=10, fig.height=7}
#| label: fig-visualize-model
#| fig-cap: "Average hourly wages by education level, gender, and age group in Canada. Wages increase with higher levels of education across all age groups."
#| echo: false
#| warning: false

@@

We are conducting a survey to understand how demographic and educational factors influence hourly wages in Canada. Your participation is important, and your responses will contribute to the research on wage distribution across various groups.

@@

Your responses are important to us in understanding wage trends in Canada. If you have any questions or would like more information about this research, please feel free to contact us at [liuyuanyi1208@gmail.com](mailto:liuyuanyi1208@gmail.com).
